### 2021-05-23 shared/analysis.tex
Optimization Step-1
WIP : QSORT

\documentclass[usenames,dvipsnames,acmsmall]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[nounderscore]{syntax}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{minted}

@@

\begin{equation}
	Obj_{1} = maximize(\sum_{i=1}^{k}{w_i * x _i}) \quad \mid \quad
	Obj_{2} = minimize(n * prob - \sum_{i=1}^{k}{w_i * x_i})
\end{equation}

@@

>>>>

\documentclass[usenames,dvipsnames,acmsmall]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[nounderscore]{syntax}
\usepackage{bussproofs}
\usepackage{mathtools}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{minted}

@@

\begin{equation}
	Objective_{2} = maximize(\sum_{i=1}^{k}{w_i * x _i})
\end{equation}

@@

\section{QuickSort Example}

Consider a pivot vector $\vec{p_{abs}}$ that \texttt{KLEE} produces over a single abstract path. We consider a $10$ element array as shown above. The $pivot$ indices for $\vec{p_{abs}}$ as choosen from a $random$ distribution.

\begin{equation}
	arr[10] = \begin{tabular}{||c|c|c|c|c|c|c|c|c|c||}
		\hline
		$a_0$ & $a_1$ & $a_2$ & $a_3$ & $a_4$ & $a_5$ & $a_6$ & $a_7$ & $a_8$ & $a_9$ \\
		\hline
	\end{tabular}
\end{equation} \\

A possible assignment of the indexes choosen as $pivot$ indices along this $abstract$ path can be as shown below.

\begin{equation}
	\vec{p_{abs}} = \begin{tabular}{||c|c|c|c|c|c||}
		\hline
		$a_9$ & $a_8$ & $a_2$ & $a_3$ & $a_8$ & $a_8$ \\
		\hline
	\end{tabular}
\end{equation} \\

For same \texttt{forall} values in $arr[10]$, we can have different random runs and on each run, the $\vec{pivot}$ vector will have a different assignment of values as indices. We are showing 5 different $\vec{pvot_{r_{j}}}$ vectors, each corresponding to a valid random run $j$.

\begin{equation}
	\vec{pvot_{r_{1}}} = \begin{tabular}{||c|c|c|c|c|c||}
		\hline
		$a_9$ & $a_4$ & $a_4$ & $a_2$ & $a_9$ & $a_9$ \\
		\hline
	\end{tabular}
\end{equation}

\begin{equation}
	\vec{pvot_{r_{2}}} = \begin{tabular}{||c|c|c|c|c||}
		\hline
		$a_9$ & $a_9$ & $a_7$ & $a_7$ & $a_7$ \\
		\hline
	\end{tabular}
\end{equation}

\begin{equation}
	\vec{pvot_{r_{3}}} = \begin{tabular}{||c|c|c|c|c|c||}
		\hline
		$a_9$ & $a_4$ & $a_1$ & $a_4$ & $a_9$ & $a_9$ \\
		\hline
	\end{tabular}
\end{equation}

\begin{equation}
	\vec{pvot_{r_{4}}} = \begin{tabular}{||c|c|c|c|c|c||}
		\hline
		$a_9$ & $a_3$ & $a_1$ & $a_9$ & $a_6$ & $a_9$ \\
		\hline
	\end{tabular}
\end{equation}

\begin{equation}
	\vec{pvot_{r_{5}}} = \begin{tabular}{||c|c|c|c|c|c||}
		\hline
		$a_9$ & $a_5$ & $a_3$ & $a_1$ & $a_9$ & $a_8$ \\
		\hline
	\end{tabular}
\end{equation}

\begin{equation}
	\vec{pvot_{r_{6}}} = \begin{tabular}{||c|c|c|c|c|c|c||}
		\hline
		$a_9$ & $a_2$ & $a_1$ & $a_9$ & $a_6$ & $a_6$ & $a_9$ \\
		\hline
	\end{tabular}
\end{equation}

\begin{equation}
	\vec{pvot_{r_{7}}} = \begin{tabular}{||c|c|c|c|c|c|c||}
		\hline
		$a_9$ & $a_9$ & $a_9$ & $a_5$ & $a_5$ & $a_9$ & $a_8$ \\
		\hline
	\end{tabular}
\end{equation} \\

For each of the random run we maintain a variable $count_j$ that tells us the total number of comparision that happened in a particular random run $j$.

We want to $assert$ the following.

\begin{equation}
	E[count_j] = n * log(n) \enspace \mid \enspace \forall j \in random \enspace runs.
\end{equation}
